---
title: "LCI_Analysis"
date: ", Last edited on `r format(Sys.time(), '%d %B %Y')`"
author: "Finn Lobnow"
output: 
  github_document:
    toc: true
    df_print: kable
---

```{r setup, include=FALSE}
library(pacman)

pacman::p_load(ggplot2, ggdark, data.table, dplyr, ggfx, viridis, ggridges, RColorBrewer, ggpubr, knitr)
filter <- dplyr::filter

knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
options(stringsAsFactors = FALSE)
theme_set(theme_bw())
theme_update(panel.grid.minor = element_blank())
```


## CELL LINES
- BDLD_27H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- BDLD_50H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- BDLD_14H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- BDLD_62H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- BDLD_57H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- BDLD_13H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- BDLD_10H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- 3E10

## PARAMETERS

``` {r}

# data_tay <- "/Volumes/TAYLOR-LAB"
# 
# # check if the path exists
# if (file.exists(data_tay)){
#   main = file.path(data_tay)
# } else {
#   # use local path
#   main = file.path("~/Documents")
# }
# 
# 
# #load tables
# TablePaths <- c(
# 
#   # MyD88-T6BM
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TRAF6-BD TRAF6/20220516 1.5nM_cl232_TRAF6_MyD88-TRAF6-BD-GFP 001/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TRAF6-BD TRAF6/20220610 1.5nM_cl232_TRAF6_MyD88-TRAF6-BD-GFP 001/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TRAF6-BD TRAF6/20220615 1.5nM_cl232_TRAF6_MyD88-TRAF6-BD-GFP 002/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TIR/20220516 1.5nM_cl244_TRAF6_TIR-GFP 001/Essential.csv.gz",
# 
#   # DHF91
#   # "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/chMyD88-DHF91-TRAF6-BD-GFP/20220401 6nM_cl221_chMyD88-DHF91-TRAF6-BD-GFP_002/Essential.csv.gz",
#   # "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/chMyD88-DHF91-TRAF6-BD-GFP/20220401 6nM_cl222_chMyD88-DHF91-TRAF6-BD-GFP_001/Essential.csv.gz",
#   # "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/chMyD88-DHF91-TRAF6-BD-GFP/20220401 6nM_cl222_chMyD88-DHF91-TRAF6-BD-GFP_002/Essential.csv.gz",
#   # "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-DHF91-TRAF6-BD TRAF6/20220516 1.5nM_cl236_TRAF6_chMyD88-DHF91-TRAF6-BD-GFP 001/Essential.csv.gz",
#   # "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-DHF91-TRAF6-BD TRAF6/20220516 1.5nM_cl236_TRAF6_chMyD88-DHF91-TRAF6-BD-GFP 002/Essential.csv.gz",
#   # "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-DHF91-TRAF6-BD TRAF6/20220516 1.5nM_cl236_TRAF6_chMyD88-DHF91-TRAF6-BD-GFP 005/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-DHF91-TRAF6-BD TRAF6/20220530 1.5nM_cl236_TRAF6_MyD88-DHF91-TRAF6-BD-GFP 001/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-DHF91-TRAF6-BD TRAF6/20220615 1.5nM_cl236_TRAF6_MyD88-DHF91-TRAF6-BD-GFP 001/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-DHF91-TRAF6-BD TRAF6/20220530 1.5nM_cl237_TRAF6_MyD88-DHF91-TRAF6-BD-GFP 001/Essential.csv.gz",
# 
#   # T6BM 3xA
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TRAF6-BD-3xA TRAF6/20220615 1.5nM_cl234_TRAF6_MyD88-TRAF6-BD-3xA-GFP 008/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-DHF91-TRAF6-BD-3xA TRAF6/20220615 1.5nM_cl238_TRAF6_MyD88-DHF91-TRAF6-BD-3xA-GFP 001/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TIR-TRAF6-BD-3xA TRAF6/20220615 1.5nM_cl242_TRAF6_MyD88-TIR-TRAF6-BD-3xA-GFP 001/Essential.csv.gz",
# 
#   # NO DD, TIR-T6BM
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TIR-TRAF6-BD TRAF6/20220610 1.5nM_cl240_TRAF6_MyD88-TIR-TRAF6-BD-GFP 001/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TIR-TRAF6-BD TRAF6/20220615 1.5nM_cl240_TRAF6_MyD88-TIR-TRAF6-BD-GFP 001/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TIR-TRAF6-BD TRAF6/20220615 1.5nM_cl240_TRAF6_MyD88-TIR-TRAF6-BD-GFP 007/Essential.csv.gz",
#   # "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TIR-TRAF6-BD TRAF6/20220516 1.5nM_cl241_TRAF6_TIR-TRAF6-BD-GFP 001/Essential.csv.gz",
# 
#   # NO T6BM
#   "/Volumes/TAYLOR-LAB/Mauriz/03_data_analysis/MyD88-TIR/20220516 1.5nM_cl244_TRAF6_TIR-GFP 001/Essential.csv.gz",
# 
#   # BDLD_27 and BDLD_14
#   "~/Documents/new_pipeline/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_10H-MyD88-TIR-TRAF6-BD-GFP TRAF6/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_13H-MyD88-TIR-TRAF6-BD-GFP TRAF6/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_57H-MyD88-TIR-TRAF6-BD-GFP TRAF6/20230602 6nM_cl321-BDLD57H_TRAF6_MyD88_001/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_57H-MyD88-TIR-TRAF6-BD-GFP TRAF6/20230602 6nM_cl321-BDLD57H_TRAF6_MyD88_002/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_62H-MyD88-TIR-TRAF6-BD-GFP TRAF6/Essential.csv.gz",
# 
#   # "/Volumes/TAYLOR-LAB/Finn/new_pipeline/pending_processing/batch_1_20230519/Output/Essential.csv.gz",
#   "~/Documents/new_pipeline/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_10H-MyD88-TIR-TRAF6-BD-GFP TRAF6/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_13H-MyD88-TIR-TRAF6-BD-GFP TRAF6/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_57H-MyD88-TIR-TRAF6-BD-GFP TRAF6/20230602 6nM_cl321-BDLD57H_TRAF6_MyD88_001/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_57H-MyD88-TIR-TRAF6-BD-GFP TRAF6/20230602 6nM_cl321-BDLD57H_TRAF6_MyD88_002/Essential.csv.gz",
#   "~/Documents/new_pipeline/BDLD_62H-MyD88-TIR-TRAF6-BD-GFP TRAF6/Essential.csv.gz",
#   "/Volumes/TAYLOR-LAB/Finn/new_pipeline/pending_processing/batch_1_20230519/Output/Essential.csv.gz"
#   )
# 
# Table <- lapply(TablePaths, fread)
# Table <- rbindlist(Table, fill=TRUE) #fill=TRUE since not all images are two color
# 
# # rename cohorts if necessary
# Table$COHORT <- gsub("*-MyD88-TIR-TRAF6-BD-GFP TRAF6", replacement = "-TIR-T6BM TRAF6", x = Table$COHORT)
# Table$COHORT <- gsub("MyD88-DHF91", replacement = "DHF91-TIR", x = Table$COHORT)
# Table$COHORT <- gsub("*TRAF6-BD", replacement = "T6BM", x = Table$COHORT)
# 
# # remove the cl028 (3E10 control from data - background was super high - not quite usable)
# Table <- Table[COHORT != "c;028-3E10-GFP"]
# 
# # get all the different cohorts in Table
# unique(Table$COHORT)
# unique(Table$LIGAND_DENSITY_CAT)
# 
# fwrite(x = Table,
#        file = "~/Documents/Github/master_thesis/scripts/LCI_ANALYSIS_files/Table.csv",
#        quote = F,
#        sep = ",")
# system("gzip -f ~/Documents/Github/master_thesis/scripts/LCI_ANALYSIS_files/Table.csv")

Table <- fread("~/Documents/Github/master_thesis/scripts/LCI_ANALYSIS_files/Table.csv.gz")

```

### Grouping and summarizing the data

#### What is the percentage of tracks recruiting TRAF6?

- group by MyD88
- define Colocalization, so the threshold at which recruitment is counted, as complementary normalized intensity ≥ 1.5
- group by Cohort, Image, Universal Track ID, and streak (grouping variable for filtering continuous frames above the threshold)
- define dwell frames as the colocalization sum
- we filter for at least 3 dwell frames


``` {r}
# # start grouping and summarizing the data
# # Find out the percentage of spots recruiting TRAF6
# Colocalisation_List <-
#   Table %>% filter(PROTEIN == "MyD88") %>%
#   arrange(UNIVERSAL_SPOT_ID) %>%
#   #threshold at which recruitment is counted
#   mutate(COLOCALIZATION = COMPLEMENTARY_NORMALIZED_INTENSITY_1 >= 1.5) %>%
#   group_by(UNIVERSAL_TRACK_ID) %>%
#   #new column which creates a grouping variable for continuous frames which are above threshold
#   mutate(STREAK = cumsum(!COLOCALIZATION)) %>%
#   #group continuous frames above threshold together
#   group_by(COHORT,
#            IMAGE,
#            UNIVERSAL_TRACK_ID,
#            STREAK) %>%
#   #number of frames that complementary protein is above threshold in a continuous stretch
#   summarise(DWELL_FRAMES = sum(COLOCALIZATION)) %>%
#   #only count 3 continuous frames as recruitment
#   filter(DWELL_FRAMES >= 3) %>%
#   # keep distinct track IDs
#   distinct(UNIVERSAL_TRACK_ID) %>%
#   as.data.table()
# 
# fwrite(x = Colocalisation_List,
#        file = "~/Documents/Github/master_thesis/scripts/LCI_ANALYSIS_files/Colocalisation_List.csv",
#        quote = F,
#        sep = ",")

Colocalisation_List <- fread("~/Documents/Github/master_thesis/scripts/LCI_ANALYSIS_files/Colocalisation_List.csv")

```


``` {r}
Track_rec <- c(unique(Colocalisation_List$UNIVERSAL_TRACK_ID))

# Filter and process data from the 'Table' dataset
#
# This code filters and processes data from the 'Table' dataset based on specific conditions,
# calculates additional metrics, and generates a summarized result as a data table.

# Step 1: Filter the dataset
# Filter rows based on specific conditions
# - PROTEIN must be "MyD88"
# - NORMALIZED_INTENSITY must be greater than or equal to 1.5
# - FRAMES_ADJUSTED must be less than or equal to 100
# - FRAMES_SINCE_LANDING must be less than or equal to 200
# - COHORT must not be "chMyD88-DHF91-TRAF6-BD-GFP"
# - COHORT must not be "DHF58v2mid_DHF58v.2"
# - COHORT must not be "MyD88-TIR"
Puncta_Cell <- Table %>%
  filter(PROTEIN == "MyD88",
         NORMALIZED_INTENSITY >= 1.5,
         FRAMES_ADJUSTED <= 100,
         FRAMES_SINCE_LANDING <= 200,
         !COHORT %in% c("chMyD88-DHF91-TRAF6-BD-GFP",
                        "DHF58v2mid_DHF58v.2",
                        "MyD88-TIR"))

# Step 2: Group the data by UNIVERSAL_TRACK_ID
# Calculate additional metrics within each group
# - LIFETIME: Maximum value of TIME_ADJUSTED
# - LIFETIME_FRAMES: Maximum value of FRAMES_ADJUSTED
# - MAX_NORMALIZED_INTENSITY: Maximum value of NORMALIZED_INTENSITY
# - MAX_COMPLEMENTARY_NORMALIZED_INTENSITY_1: Maximum value of COMPLEMENTARY_NORMALIZED_INTENSITY_1
# - RECRUITEMENT: Assigns "+ve" if UNIVERSAL_TRACK_ID is in Track_rec, otherwise "-ve"
Puncta_Cell <- Puncta_Cell %>%
  group_by(UNIVERSAL_TRACK_ID) %>%
  mutate(LIFETIME = max(TIME_ADJUSTED),
         LIFETIME_FRAMES = max(FRAMES_ADJUSTED),
         MAX_NORMALIZED_INTENSITY = max(NORMALIZED_INTENSITY),
         MAX_COMPLEMENTARY_NORMALIZED_INTENSITY_1 = max(COMPLEMENTARY_NORMALIZED_INTENSITY_1),
         RECRUITEMENT = case_when(UNIVERSAL_TRACK_ID %in% Track_rec ~ "+ve", TRUE ~ "-ve"))

# Step 3: Filter the dataset again
# Filter rows based on additional conditions
# - LIFETIME_FRAMES must be greater than or equal to 3
# - FRAMES_ADJUSTED must be equal to 0
Puncta_Cell <- Puncta_Cell %>%
  filter(LIFETIME_FRAMES >= 3,
         FRAMES_ADJUSTED == 0)

# Step 4: Group the data by COHORT, IMAGE, and CELL
# Calculate the final summarized metrics within each group
# - T6p: Ratio of the count of positive RECRUITEMENT to the total count of RECRUITEMENT values (positive and negative)
# - T6n: Ratio of the count of negative RECRUITEMENT to the total count of RECRUITEMENT values (positive and negative)
Puncta_Cell <- Puncta_Cell %>%
  group_by(COHORT, IMAGE, CELL) %>%
  summarize(T6p = sum(RECRUITEMENT == "+ve") / (sum(RECRUITEMENT == "+ve") + sum(RECRUITEMENT == "-ve")),
            T6n = sum(RECRUITEMENT == "-ve") / (sum(RECRUITEMENT == "+ve") + sum(RECRUITEMENT == "-ve")))

# Convert the result to a data table
Puncta_Cell <- as.data.table(Puncta_Cell)


#create the stats variable to add mean etc. to plots
# Stats<- Stats <- Puncta_Cell %>% 
#   group_by(COHORT) %>%
#   mutate(SD_T6p=sd(T6p)) %>% 
#   summarize(T6p=mean(T6p),
#             SEM_T6p=mean(SD_T6p/sqrt(n()))) %>% 
#   as.data.table()

# Calculate statistics using the median and median absolute deviation (MAD)
# This code calculates statistics using the median and median absolute deviation (MAD) for the 'T6p' variable in the 'Puncta_Cell' dataset.
# The statistics include the median and MAD for each 'COHORT' group.

# Step 1: Calculate the median and median absolute deviation (MAD) for 'T6p' within each 'COHORT' group
# Group the data by 'COHORT' and calculate the median and MAD for 'T6p' within each group
Stats <- 
  Stats<- 
  Puncta_Cell %>%
  group_by(COHORT) %>%
  summarize(T6p = median(T6p),
            MAD_T6p = median(abs(T6p - median(T6p)))) %>%
  # Convert the result to a data table
  as.data.table()

# #Add stats for the images taken to clean up violin
# Replicates<- Puncta_Cell %>% 
#   group_by(IMAGE,COHORT) %>% 
#   summarize(T6p=mean(T6p)) %>% 
#   as.data.table()  

# Step 1: Calculate the median 'T6p' for each combination of 'IMAGE' and 'COHORT' groups
# Group the data by 'IMAGE' and 'COHORT' and calculate the median 'T6p' within each group
Replicates <- Puncta_Cell %>%
  group_by(IMAGE, COHORT) %>%
  summarize(T6p = median(T6p))

# Step 2: Convert the result to a data table
Replicates <- as.data.table(Replicates)
```


### Plot the percentage of tracks recruiting TRAF6 per cell as a violin

Percentage of Spots above threshold Lifetime/ Max Intensity per Cell per Cell line

``` {r, fig.width = 25}
Puncta_Cell %>%
  ggplot(aes(x=COHORT, y=T6p*100)) +
  geom_violin(alpha=0.75, 
              aes(fill = COHORT),
              # fill="gray", 
              scale = "width") +
  geom_jitter(data=Replicates,
              color="black") +
  geom_errorbar(data = Stats,aes(x = COHORT, 
                                 y= T6p*100, 
                                 # ymin = T6p-SEM_T6p, 
                                 # ymax = T6p+SEM_T6p
                                 ymin = T6p*100-MAD_T6p,
                                 ymax = T6p*100+MAD_T6p
                                 ),
                color="black", 
                width=0.4) +
  stat_summary(data=Stats,
               fun = "mean",
               geom = "crossbar", 
               width = 0.3,
               linewidth = 0.4,
               position= position_dodge(width = 1),
               colour = "black")+
  labs(x="Cell Lines", y="Percentage of Puncta recruiting TRAF6 per Cell") +
  theme_classic() + theme(legend.position = "none") +
  theme(axis.text = element_text(size = 20, face = "bold"),
        axis.title = element_text(size = 25, face = "bold"))

```

### Plot the MyD88 intensity over TRAF6 intensity using geom_hex

``` {r}
MyD88Int <-Table %>% 
  filter(PROTEIN=="MyD88",
         FRAMES_ADJUSTED<=100,
         FRAMES_SINCE_LANDING<=200,
         COHORT!="chMyD88-DHF91-TRAF6-BD-GFP",
         COHORT!="DHF58v2mid_DHF58v.2",
         COHORT!="MyD88-TIR",
         NORMALIZED_INTENSITY>=1.5) %>% 
  group_by(UNIVERSAL_TRACK_ID) %>% 
  mutate(LIFETIME = max(TIME_ADJUSTED),
         LIFETIME_FRAMES = max(FRAMES_ADJUSTED),
         MAX_NORMALIZED_INTENSITY = max(NORMALIZED_INTENSITY),
         MAX_COMPLEMENTARY_NORMALIZED_INTENSITY_1 = max(COMPLEMENTARY_NORMALIZED_INTENSITY_1)) %>% 
  filter(LIFETIME_FRAMES>=3, 
         FRAMES_ADJUSTED==0) %>% as.data.table()

ggplot(data = MyD88Int,
  aes(x = MAX_NORMALIZED_INTENSITY,
      y = MAX_COMPLEMENTARY_NORMALIZED_INTENSITY_1)) +
  geom_hex(bins=15) +
  scale_x_continuous(limits=c(0, 50)) +
  scale_y_continuous(limits=c(0, 20)) +
  facet_wrap(~COHORT
             #, ncol = 1
             )+
  scale_fill_viridis(trans = 'log10') +
  geom_smooth(method = "lm", se = FALSE) +
  stat_cor(method="spearman", color="red")+
  labs(x="Normalized Max Intensity of MyD88",
       y="Normalized Max Intensity of TRAF6")+
  theme_classic() +
  theme(legend.position = "bottom")
```

### Plot the MyD88 intensity over TRAF6 intensity using geom_path

``` {r}
TRAF6col <- Table %>%
  filter(PROTEIN=="MyD88") %>% 
  mutate(COMPLEMENTARY_NORMALIZED_INTENSITY_1 = round(COMPLEMENTARY_NORMALIZED_INTENSITY_1)) %>% 
  group_by(COHORT, COMPLEMENTARY_NORMALIZED_INTENSITY_1) %>% 
 summarize(NORMALIZED_INTENSITY = mean(NORMALIZED_INTENSITY)) %>%
  as.data.table()

ggplot(TRAF6col, aes(x = NORMALIZED_INTENSITY,
                     y = COMPLEMENTARY_NORMALIZED_INTENSITY_1,
                     col = COHORT)) +
  geom_path() + 
  scale_x_continuous(limits = c(0,50)) +
  scale_y_continuous(limits = c(0,10)) +
  labs(x="Normalized Intensity of MyD88",
       y="Normalized Intensity of TRAF6") + 
  theme_classic() +
  facet_wrap(~COHORT)
```

### Percentage of puncta at distinct size/ Lifetime to recruit TRAF6

``` {r}
PCTTRAF6 <- Table %>% 
  filter(PROTEIN=="MyD88", 
         NORMALIZED_INTENSITY >= 1.5,
         FRAMES_ADJUSTED <= 100,
         FRAMES_SINCE_LANDING <= 200,
         COHORT!="chMyD88-DHF91-TRAF6-BD-GFP",
         COHORT!="DHF58v2mid_DHF58v.2",
         #COHORT!="MyD88-TIR"
         ) %>% 
  group_by(UNIVERSAL_TRACK_ID) %>% 
  mutate(LIFETIME = max(TIME_ADJUSTED),
         LIFETIME_FRAMES = max(FRAMES_ADJUSTED),
         MAX_NORMALIZED_INTENSITY = max(NORMALIZED_INTENSITY),
         MAX_COMPLEMENTARY_NORMALIZED_INTENSITY_1 = max(COMPLEMENTARY_NORMALIZED_INTENSITY_1),
         RECRUITEMENT = case_when(UNIVERSAL_TRACK_ID %in% Track_rec ~ "+ve", TRUE ~ "-ve"),
         MAX_NORMALIZED_INTENSITY=round(MAX_NORMALIZED_INTENSITY),
         LIFETIME=round(LIFETIME)) %>% 
  filter(LIFETIME_FRAMES >= 3, FRAMES_ADJUSTED == 0) %>% 
  as.data.table()

Stats <- PCTTRAF6 %>% 
  group_by(COHORT) %>% 
  summarise(MAX_NORMALIZED_INTENSITY = mean(MAX_NORMALIZED_INTENSITY),
            LIFETIME = mean(LIFETIME)) %>% 
  as.data.table()

kable(Stats)
```

### Percentage of MYD88 tracks that recruit TRAF6 vs MyD88 intensity


``` {r}
#TRAF6 at different Max normalized Intensities

PCTTRAF6Int<-
  PCTTRAF6 %>% 
  group_by(
    MAX_NORMALIZED_INTENSITY,
    COHORT
  ) %>% 
  filter(n() >= 3) %>%
  summarize(
    T6p=sum(RECRUITEMENT=="+ve")/(sum(RECRUITEMENT=="+ve")+sum(RECRUITEMENT=="-ve")),
    T6n=sum(RECRUITEMENT=="-ve")/(sum(RECRUITEMENT=="+ve")+sum(RECRUITEMENT=="-ve"))
  ) %>%
  as.data.table()

ggplot(
  data=PCTTRAF6Int,
  aes(
    x=MAX_NORMALIZED_INTENSITY,
    y=T6p*100,
    fill=COHORT
  )
)+
  geom_smooth(
    level=0.90,
    color="black"
  )+
  scale_x_continuous(
    limits = c(0,50)
  )+
  scale_y_continuous(
    limits=c(0,100)
  )+
  geom_jitter(
    color="black"
  )+
  facet_wrap(
    ~COHORT
  )+
  labs(
    x="Max Normalized Intensity of Tracks",
    y="% of Tracks recruiting TRAF6"
  )+
  theme_bw()
```

### Plot the percentage of TRAF6 recruitement at different Lifetimes


``` {r}
PCTTRAF6 <- PCTTRAF6[COHORT != "c;028-3E10-GFP"]

PCTTRAF6LT <- PCTTRAF6 %>% 
  group_by(LIFETIME, COHORT) %>% 
  filter(n() >= 3) %>%
  summarize(T6p=sum(RECRUITEMENT=="+ve")/(sum(RECRUITEMENT=="+ve")+sum(RECRUITEMENT=="-ve")),
            T6n=sum(RECRUITEMENT=="-ve")/(sum(RECRUITEMENT=="+ve")+sum(RECRUITEMENT=="-ve"))) %>%
  as.data.table()


ggplot(data=PCTTRAF6LT,
       aes(x = LIFETIME, y = T6p, fill = COHORT)) +
  geom_smooth(level = 0.90, color = "black") +
  scale_x_continuous(limits = c(0,400)) +
  geom_jitter(color = "black") +
  facet_wrap(~COHORT) +
  labs(x = "Lifetime of Tracks",
       y = "% of Tracks recruiting TRAF6") +
  theme_bw()

ggplot(PCTTRAF6, aes(x = LIFETIME, y = ..ndensity.., fill = COHORT)) +
  geom_histogram(binwidth = 5,
                 colour="black",
                 alpha=0.75) +
  #geom_vline(data = Stats, aes(xintercept = LIFETIME),
  #           color="black", 
  #           linetype="dashed", 
  #           linewidth=1) +
  scale_x_continuous(limits = c(0,400)) +
  facet_wrap(~COHORT) +
  labs(x = "Lifetime of Tracks",
       y = "Density") +
  theme_bw()
# get mean / median values written down
```