---
title: "LCI_Analysis"
date: ", Last edited on `r format(Sys.time(), '%d %B %Y')`"
author: "Finn Lobnow"
output: 
  github_document:
    toc: true
    df_print: kable
---

```{r setup, include=FALSE}
library(pacman)

pacman::p_load(ggplot2, ggdark, data.table, dplyr, ggfx, viridis, ggridges, RColorBrewer, ggpubr, knitr)
filter <- dplyr::filter

knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
options(stringsAsFactors = FALSE)
theme_set(theme_bw())
theme_update(panel.grid.minor = element_blank())
```


## CELL LINES
- BDLD_27H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- BDLD_50H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- BDLD_14H-MyD88-TIR-TRAF6-BD-GFP TRAF6
- 3E10

## PARAMETERS

``` {r}

data_tay <- "/Volumes/TAYLOR-LAB/"

# check if the path exists 
if (file.exists(data_tay)){
  main = file.path(data_tay)
} else { 
  # use local path
  main = file.path("~/Documents")
}

PARAMETERS_PATH = file.path(main, "/new_pipeline/pending_processing/batch_1_20230519/Input/parameter_tables/")

parameters_lst_files = list.files(PARAMETERS_PATH)
constants          = fread(file.path(PARAMETERS_PATH, "constants.csv"))
dark_frames        = fread(file.path(PARAMETERS_PATH, "dark_frames.csv"))
directories        = fread(file.path(PARAMETERS_PATH, "directories.csv"))
exclusion_channels = fread(file.path(PARAMETERS_PATH, "exclusion_channels.csv"))
images             = fread(file.path(PARAMETERS_PATH, "images.csv"))

```

``` {r}
kable(constants)
kable(dark_frames)
kable(directories)
kable(exclusion_channels)
kable(images)
```

``` {r}
#load tables
TablePaths <- c(
  file.path(main, "Mauriz_R/MyD88-TRAF6-BD TRAF6/20220516 1.5nM_cl232_TRAF6_MyD88-TRAF6-BD-GFP 001/Essential.csv.gz"),
  file.path(main, "Mauriz_R/MyD88-TRAF6-BD TRAF6/20220610 1.5nM_cl232_TRAF6_MyD88-TRAF6-BD-GFP 001/Essential.csv.gz"),
  file.path(main, "Mauriz_R/MyD88-TRAF6-BD TRAF6/20220615 1.5nM_cl232_TRAF6_MyD88-TRAF6-BD-GFP 002/Essential.csv.gz"),
  file.path(main, "new_pipeline/pending_processing/batch_1_20230519/Output/Essential.csv.gz")
  
  # BDLD - Bacterial Death-Like Domains
  # file.path(main, "/Finn/new_pipeline/pending_processing/batch_1_20230519/Output/Essential.csv.gz"),
  # file.path(main, "/Finn/new_pipeline/pending_processing/batch_2_20230602/Processing/06_Colocalization/BDLD_62H-MyD88-TIR-TRAF6-BD-GFP TRAF6/20230602 6nM_cl318-BDLD62H_TRAF6_MyD88_001/Essential.csv.gz")
  # "~/Documents/new_pipeline/pending_processing/batch_1_20230519/Output/Essential.csv.gz")
  )

Table <- lapply(TablePaths, fread)
Table <- rbindlist(Table, fill=TRUE) #fill=TRUE since not all images are two color

```


``` {r}
#start grouping and summarizing the data
#Find out the percentage of spots recruiting TRAF6
Colocalisation_List <-
  Table %>% filter(PROTEIN == "MyD88") %>% 
  arrange(UNIVERSAL_SPOT_ID) %>% 
  #threshold at which recruitment is counted
  mutate(COLOCALIZATION = COMPLEMENTARY_NORMALIZED_INTENSITY_1 >= 1.5) %>% 
  group_by(UNIVERSAL_TRACK_ID) %>%
  #new column which creates a grouping variable for continuous frames which are above threshold
  mutate(STREAK = cumsum(!COLOCALIZATION)) %>%
  #group continuous frames above threshold together
  group_by(COHORT,IMAGE,UNIVERSAL_TRACK_ID,STREAK) %>% 
  #number of frames that complementary protein is above threshold in a continuous stretch
  summarise(DWELL_FRAMES = sum(COLOCALIZATION)) %>% 
  #only count 3 continuous frames as recruitment
  filter(DWELL_FRAMES >= 1) %>% 
  distinct(UNIVERSAL_TRACK_ID) %>% 
  as.data.table()
```


``` {r}
Track_rec <- c(unique(Colocalisation_List$UNIVERSAL_TRACK_ID))

Puncta_Cell<-Table %>% 
  filter(PROTEIN=="MyD88",
         NORMALIZED_INTENSITY >= 1.5,
         FRAMES_ADJUSTED <= 100,
         FRAMES_SINCE_LANDING<=200,
         COHORT!="chMyD88-DHF91-TRAF6-BD-GFP",
         COHORT!="DHF58v2mid_DHF58v.2",
         COHORT!="MyD88-TIR") %>% 
  group_by(UNIVERSAL_TRACK_ID) %>% 
  mutate(LIFETIME=max(TIME_ADJUSTED),
         LIFETIME_FRAMES=max(FRAMES_ADJUSTED),
         MAX_NORMALIZED_INTENSITY=max(NORMALIZED_INTENSITY),
         MAX_COMPLEMENTARY_NORMALIZED_INTENSITY_1=max(COMPLEMENTARY_NORMALIZED_INTENSITY_1),
         RECRUITEMENT=case_when(UNIVERSAL_TRACK_ID %in% Track_rec ~ "+ve", TRUE ~ "-ve")) %>% 
  filter(LIFETIME_FRAMES>=3,
         FRAMES_ADJUSTED==0) %>%
  group_by(COHORT,IMAGE,CELL) %>%
  summarize(T6p=sum(RECRUITEMENT=="+ve")/(sum(RECRUITEMENT=="+ve")+sum(RECRUITEMENT=="-ve")),
            T6n=sum(RECRUITEMENT=="-ve")/(sum(RECRUITEMENT=="+ve")+sum(RECRUITEMENT=="-ve"))) %>% 
  as.data.table()

#create the stats variable to add mean etc. to plots
Stats<- Stats <- Puncta_Cell %>% 
  group_by(COHORT) %>%
  mutate(SD_T6p=sd(T6p)) %>% 
  summarize(T6p=mean(T6p),
            SEM_T6p=mean(SD_T6p/sqrt(n()))) %>% 
  as.data.table()

#Add stats for the images taken to clean up violin
Replicates<- Puncta_Cell %>% 
  group_by(IMAGE,COHORT) %>% 
  summarize(T6p=mean(T6p)) %>% 
  as.data.table()  
```


### Plot the percentage of tracks recruiting TRAF6 per cell as a violin

Percentage of Spots above threshold Lifetime/ Max Intensity per Cell per Cell line

``` {r}
ggplot(data=Puncta_Cell,aes(x=COHORT, y=T6p))+
  geom_violin(alpha=0.75, fill="gray", 
              scale = "width")+
  geom_jitter(data=Replicates,
              color="black")+
  geom_errorbar(data = Stats,aes(x = COHORT, y= T6p, ymin = T6p-SEM_T6p, ymax = T6p+SEM_T6p),
                color="black", 
                width=0.4) +
  stat_summary(data=Stats,
               fun = "mean",
               geom = "crossbar", 
               width = 0.3,
               linewidth = 0.4,
               position= position_dodge(width = 1),
               colour = "black")+
  labs(x="Cell Lines", y="Percentage of Puncta recruiting TRAF6 per Cell") +
  theme_classic()

```

### Plot the MyD88 intensity over TRAF6 intensity using geom_hex

``` {r}
MyD88Int <-Table %>% 
  filter(PROTEIN=="MyD88",
         FRAMES_ADJUSTED<=100,
         FRAMES_SINCE_LANDING<=200,
         COHORT!="chMyD88-DHF91-TRAF6-BD-GFP",
         COHORT!="DHF58v2mid_DHF58v.2",
         COHORT!="MyD88-TIR",
         NORMALIZED_INTENSITY>=1.5) %>% 
  group_by(UNIVERSAL_TRACK_ID) %>% 
  mutate(LIFETIME = max(TIME_ADJUSTED),
         LIFETIME_FRAMES = max(FRAMES_ADJUSTED),
         MAX_NORMALIZED_INTENSITY = max(NORMALIZED_INTENSITY),
         MAX_COMPLEMENTARY_NORMALIZED_INTENSITY_1 = max(COMPLEMENTARY_NORMALIZED_INTENSITY_1)) %>% 
  filter(LIFETIME_FRAMES>=3, 
         FRAMES_ADJUSTED==0) %>% as.data.table()
```

```{r}
ggplot(data = MyD88Int,
  aes(x = MAX_NORMALIZED_INTENSITY,
      y = MAX_COMPLEMENTARY_NORMALIZED_INTENSITY_1)) +
  geom_hex(bins=15) +
  scale_x_continuous(limits=c(0, 50)) +
  scale_y_continuous(limits=c(0, 20)) +
  facet_wrap(~COHORT)+
  scale_fill_viridis(trans = 'log10') +
  geom_smooth(method = "lm", se = FALSE) +
  stat_cor(method="spearman", color="red")+
  labs(x="Normalized Max Intensity of MyD88",
       y="Normalized Max Intensity of TRAF6")+
  theme_classic()
```

### Plot the MyD88 intensity over TRAF6 intensity using geom_path

``` {r}
TRAF6col <- Table %>%
  filter(PROTEIN=="MyD88") %>% 
  mutate(COMPLEMENTARY_NORMALIZED_INTENSITY_1 = round(COMPLEMENTARY_NORMALIZED_INTENSITY_1)) %>% 
  group_by(COHORT, COMPLEMENTARY_NORMALIZED_INTENSITY_1) %>% 
  summarize(NORMALIZED_INTENSITY = mean(NORMALIZED_INTENSITY)) %>%
  as.data.table()

ggplot(TRAF6col, aes(x = NORMALIZED_INTENSITY,
                     y = COMPLEMENTARY_NORMALIZED_INTENSITY_1,
                     col = COHORT)) +
  geom_path() + 
  scale_x_continuous(limits = c(0,50)) +
  scale_y_continuous(limits = c(0,10)) +
  labs(x="Normalized Intensity of MyD88",
       y="Normalized Intensity of TRAF6") + 
  theme_classic()
```

### Percentage of puncta at distinct size/ Lifetime to recruit TRAF6

``` {r}
PCTTRAF6 <- Table %>% 
  filter(PROTEIN=="MyD88", 
         NORMALIZED_INTENSITY >= 1.5,
         FRAMES_ADJUSTED <= 100,
         FRAMES_SINCE_LANDING <= 200,
         COHORT!="chMyD88-DHF91-TRAF6-BD-GFP",
         COHORT!="DHF58v2mid_DHF58v.2",
         COHORT!="MyD88-TIR") %>% 
  group_by(UNIVERSAL_TRACK_ID) %>% 
  mutate(LIFETIME = max(TIME_ADJUSTED),
         LIFETIME_FRAMES = max(FRAMES_ADJUSTED),
         MAX_NORMALIZED_INTENSITY = max(NORMALIZED_INTENSITY),
         MAX_COMPLEMENTARY_NORMALIZED_INTENSITY_1 = max(COMPLEMENTARY_NORMALIZED_INTENSITY_1),
         RECRUITEMENT = case_when(UNIVERSAL_TRACK_ID %in% Track_rec ~ "+ve", TRUE ~ "-ve"),
         MAX_NORMALIZED_INTENSITY=round(MAX_NORMALIZED_INTENSITY),
         LIFETIME=round(LIFETIME)) %>% 
  filter(LIFETIME_FRAMES >= 3, FRAMES_ADJUSTED == 0) %>% 
  as.data.table()

Stats <- PCTTRAF6 %>% 
  group_by(COHORT) %>% 
  summarise(MAX_NORMALIZED_INTENSITY = mean(MAX_NORMALIZED_INTENSITY),
            LIFETIME = mean(LIFETIME)) %>% 
  as.data.table()

kable(Stats)
```

### Percentagw of TRAF6 at different Max normalized Intensities

``` {r}
PCTTRAF6Int<-
  PCTTRAF6 %>% 
  group_by(
    MAX_NORMALIZED_INTENSITY,
    COHORT
  ) %>% 
  filter(n() >= 3) %>%
  summarize(
    T6p=sum(RECRUITEMENT=="+ve")/(sum(RECRUITEMENT=="+ve")+sum(RECRUITEMENT=="-ve")),
    T6n=sum(RECRUITEMENT=="-ve")/(sum(RECRUITEMENT=="+ve")+sum(RECRUITEMENT=="-ve"))
  ) %>%
  as.data.table()

ggplot(
  data=PCTTRAF6Int,
  aes(
    x=MAX_NORMALIZED_INTENSITY,
    y=T6p*100,
    fill=COHORT
  )
)+
  geom_smooth(
    level=0.90,
    color="black"
  )+
  scale_x_continuous(
    limits = c(0,50)
  )+
  scale_y_continuous(
    limits=c(0,100)
  )+
  geom_jitter(
    color="black"
  )+
  facet_wrap(
    ~COHORT
  )+
  labs(
    x="Max Normalized Intensity of Tracks",
    y="% of Tracks recruiting TRAF6"
  )+
  theme_bw()
```